Large scale risks from agricultural pesticides in small streams

### 2017-05-02 article.tex
comments from rs

% size
We did not find a statistically significant relationship between pesticide pollution and catchment size (Hypothesis 2). 
However, previous studies showed that small streams are more polluted than bigger streams \citep{schulz_field_2004,stehle_pesticide_2015,knauer_pesticides_2016}.
This can be explained by the relatively short gradient of catchment sizes in our dataset, with most of the streams with catchments above $10~km^2$ and below $100~km^2$ (Figure~\ref{fig:fig3}, top).
For example, the gradient of \citet{schulz_field_2004} covered 6 orders of magnitude. 
Although there is a relationship between catchment size and stream size (Supplemental Figure~S11), this might be also influenced by geology and precipitation regime. 
Therefore, our results cannot be directly translated to stream size.

>>>>

% size
We did not find a statistically significant relationship between pesticide pollution and catchment size (Hypothesis 2). 
However, previous studies showed that small streams are more polluted than bigger streams \citep{schulz_field_2004,stehle_pesticide_2015,knauer_pesticides_2016}.
This can be explained by the relatively short gradient of catchment sizes in our dataset, with most of the streams with catchments above $10~km^2$ and below $100~km^2$ (Figure~\ref{fig:fig3}, top).
For example, the gradient of \citet{schulz_field_2004} covered 6 orders of magnitude. 
Although catchment size and stream size were strongly correlated (Supplemental Figure~S11), other factors such as geology, hydrology and precipitation regime also determine the stream size. 
Therefore, translating our results to stream size bears uncertainties.
